Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board

### 2015-04-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update latex

Figure~\ref{HRR} shows the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires. In each graph, the replicate heat release time histories are overlaid to give a sense of the experimental repeatability for each fuel.

\begin{figure}[p]
  \centering
  \includegraphics[width=4.5in]{../Figures/Fig3}\\
  \includegraphics[width=4.5in]{../Figures/Fig4}\\
  \includegraphics[width=4.5in]{../Figures/Fig5}\\
  \caption[Heat release rates for the natural gas, gasoline and foam fires]{Heat release rates for the natural gas, gasoline, and foam fires.}
  \label{HRR}
\end{figure}

On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.  A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.  In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95~\%.

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0m_Reps_Avg}\\
	\caption[Plume temperatures along the centerline of the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{TC_Plume_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_61m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_31m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_15m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0m_Reps_Avg}\\
	\caption[Wall Temperatures along the centerline of the natural gas fueled burner]{Wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Cent_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0m_Reps_Avg}\\
	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Edge_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0m_Reps_Avg}\\
	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Back_Center_TWNG_comp}
\end{figure}

@@

Figure~\ref{NCTW_Surf_Center_comp} shows the temperatures of the array of thermocouples located along the vertical centerline of the burners for each of the three fuels.  The beads of the thermocouples were installed in the wall and were flush with the wall surface. In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown. Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m. As in the data analysis for the source fires, the peak averages were based on a 30 s period bounding the peak for the natural gas and gasoline fires.  A 15 s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Offset_Avg}\\

	\caption[Composite graph of the wall temperatures along the edge of the burners]{Composite graph of the wall temperatures along the edge of the burners for each fuel. The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall. Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_Surf_Edge_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Back_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Back_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Back_Center_Avg}\\

	\caption[Composite graph of the backside wall temperatures along the center of the burners]{Composite graph of the backside wall temperatures along the vertical centerline of the burners for each fuel. The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall. Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_Back_Cent_comp}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Center_Avg} \\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Center_Avg} \\

	\caption[Wall heat flux along the centerline of the burners]{Wall heat fluxes along the centerline of the burners.  The heat fluxes are averages of replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_HF_Center_Comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Offset_Avg} \\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Offset_Avg} \\

	\caption[Wall heat flux along the edge of the burners]{Wall heat fluxes along the edge of the burners.  The heat fluxes are averages of replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_HF_Edge_Comp}
\end{figure}

>>>>

Figures~\ref{HRR}-\ref{HRR2} show the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires. In each graph, the replicate heat release time histories are overlaid to give a sense of the experimental repeatability for each fuel.

\begin{figure}[h!]
  \centering
  \includegraphics[width=4.5in]{../Figures/ST_NG_HRR}\\
  \includegraphics[width=4.5in]{../Figures/ST_Gas_HRR}\\
  \caption[Heat release rates for the natural gas and gasoline foam fires]{Heat release rates for the natural gas and gasoline fires.}
  \label{HRR}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=4.5in]{../Figures/ST_PUF_HRR}\\
  \caption[Heat release rates for the polyurethane foam fires]{Heat release rates for the polyurethane foam fires.}
  \label{HRR2}
\end{figure}

On each fuel’s averaged heat release rate curve, the filled area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.  A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.  In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95~\%.

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0m_Reps_Avg}\\
	\caption[Plume temperatures along the centerline of the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
	\label{TC_Plume_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p61m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p31m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p15m_Reps_Avg}\\
		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0m_Reps_Avg}\\
	\caption[Wall Temperatures along the centerline of the natural gas fueled burner]{Wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Cent_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0m_Reps_Avg}\\
	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Surf_Edge_TWNG_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p61m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p31m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p15m_Reps_Avg}\\
	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0m_Reps_Avg}\\
	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner. The temperatures are averages of two replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
	\label{TC_Back_Center_TWNG_comp}
\end{figure}

@@

Figure~\ref{NCTW_Surf_Center_comp} shows the temperatures of the array of thermocouples located along the vertical centerline of the burners for each of the three fuels.  The beads of the thermocouples were installed in the wall and were flush with the wall surface. In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown. Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m. As in the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.  A 15~s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Offset_Avg}\\
	\caption[Composite graph of the wall temperatures along the edge of the burners]{Composite graph of the wall temperatures along the edge of the burners for each fuel. The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall. Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_Surf_Edge_comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Back_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Back_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Back_Center_Avg}\\
	\caption[Composite graph of the backside wall temperatures along the center of the burners]{Composite graph of the backside wall temperatures along the vertical centerline of the burners for each fuel. The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall. Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_Back_Cent_comp}
\end{figure}

@@

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Center_Avg} \\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Center_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Center_Avg} \\
	\caption[Wall heat flux along the centerline of the burners]{Wall heat fluxes along the centerline of the burners.  The heat fluxes are averages of replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_HF_Center_Comp}
\end{figure}

\begin{figure}[p]
	\centering
	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Offset_Avg} \\
	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Offset_Avg}\\
	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Offset_Avg} \\
	\caption[Wall heat flux along the edge of the burners]{Wall heat fluxes along the edge of the burners.  The heat fluxes are averages of replicate experiments. Each graph displays data from a different distance between the edge of the burner and the instrumented wall.  Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
	\label{NCTW_HF_Edge_Comp}
\end{figure}
